---
title: "Solutions for Homework 6"
author: "Jiajun Tao"
date: "2022-11-29"
output: github_document
---

```{r, include = FALSE,message=FALSE,warning=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	message = FALSE,
  fig.width = 8,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


### Problem 1

First, we download the data.

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


### Problem 2

First, we import the data.

```{r}
homicides_df = read_csv("data/homicide-data.csv") 

homicides_df
```

Then we created a `city_state` variable, and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. Limit the analysis those for whom `victim_race` is white or black. Be sure that `victim_age` is numeric.

```{r}
homicides_df=
  homicides_df %>% 
  mutate(
    city_state = str_c(city, ", ", state),
    whether_solved = ifelse(disposition %in% c("Closed without arrest", "Open/No arrest"), 0, 1)
  ) %>% 
  filter(!city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")) %>% 
  filter(victim_race %in% c("Black", "White")) %>% 
  filter(victim_age != "Unknown") %>% 
  mutate(victim_age = as.numeric(victim_age),
         victim_sex = as.factor(victim_sex),
         victim_race = fct_relevel(victim_race,"White"))

homicides_df
```

For the city of Baltimore, MD, use the `glm` function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. Save the output of `glm` as an R object; apply the `broom::tidy` to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.

```{r}
fit_logistic = 
  homicides_df %>% 
  filter(city == "Baltimore") %>% 
  glm(whether_solved ~ victim_age + victim_sex + victim_race, data = ., family = binomial())

fit_logistic %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate),
         lower = exp(confint(fit_logistic)[,1]),
         upper = exp(confint(fit_logistic)[,2])) %>% 
  filter(term == "victim_sexMale") %>% 
  select(OR, lower, upper) %>% 
  knitr::kable(digits = 3)
```

We can see that homicides in which the victim is male are significantly less like to be resolved than those in which the victim is female in Baltimore.

Now run `glm` for each of the cities in the dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims. 

```{r}
logistic_function = function(demographics){
  
  logistic_fit = glm(whether_solved ~ victim_age + victim_sex + victim_race, data = demographics, family = binomial())
  
  logistic_fit %>% 
    broom::tidy() %>% 
    mutate(OR = exp(estimate),
           lower = exp(confint(logistic_fit)[,1]),
           upper = exp(confint(logistic_fit)[,2])) %>% 
    filter(term == "victim_sexMale") %>% 
    select(OR, lower, upper) 
}

logistic_df = 
  homicides_df %>% 
  select(city_state,victim_age, victim_race, victim_sex, whether_solved) %>% 
  nest(demographics = victim_age:whether_solved) %>% 
  mutate(
    logistic_fit = purrr::map(demographics, logistic_function)
  ) %>% 
  select(-demographics) %>% 
  unnest(logistic_fit)

logistic_df
```

Finally we create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR.

```{r}
logistic_df %>% 
  mutate(
    city_state = fct_reorder(city_state, OR)
  ) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_errorbar(aes(ymin = lower, ymax = upper)) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(
    title = "Odds ratio for solving homicides comparing male victims to female victims",
    x = "City",
    y = "Estimated OR"
  )
```

